---
title: "Analysis Bachelor Thesis"
author: "Tamara Keßler"
date: "17 5 2020"
output: html_document
---

```{r supress warnings, echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, # supress warnings per default 
  message = FALSE  # supress messages per default 
)
```


```{r libraries, echo=FALSE}
library(tidyverse)
library(ggplot2)
library(mousetrap)
library(readbulk)
#library(cowplot)
```

```{r ggplot theme, echo=FALSE}
theme_set(theme_minimal() +
  theme(
    axis.line = element_line(colour = "black"),
    axis.ticks = element_line(colour = "black"),
    axis.text = element_text(colour = "black"),
    panel.border = element_rect(colour = "black", fill=NA)
  ))

options(width=90, scipen = 999)
```

```{r load data, echo=FALSE}

raw_data <- read_opensesame("raw_data")
mt_data <- mt_import_mousetrap(raw_data)

```

# Pre-Processing

```{r get correctness & ratios, echo = FALSE}

correctness_data <- mt_data %>% 
  mt_subset(Condition != "Example") %>%
  mt_reshape(
    use2 = "data", 
    use2_variables = c("correct", "Condition", "Exemplar"), 
    aggregate = FALSE
  ) 

#print(correctness_data)

correctness_conditions <- correctness_data %>% 
  group_by(Condition) %>%
  summarise(
    correct_mean = mean(correct), correct_sd = sd(correct)
  )

#print(correctness_conditions)

correctness_exemplars <- correctness_data %>%
  group_by(Exemplar) %>%
  summarise(
    correct_mean = mean(correct), correct_sd = sd(correct)
  )

#print(correctness_exemplars)

#write.table(correctness_exemplars, "Correctness_Ratios_Exemplars", sep = ",")

```

```{r filtering, echo=FALSE}

mt_data <- mt_subset(mt_data, Condition!="Example" & correct==1)
```

```{r spatial normalisations, echo=FALSE}

# Re-Mapping trajectories
mt_data <- mt_remap_symmetric(mt_data)

# Align cursor's starting position by shifting trajectories
mt_data <- mt_align_start(mt_data, start=c(0,0))
```

```{r temporal normalisations, echo=FALSE}

# Apply time-normalisation to aggregate trajectories/compare them statistically
normalised_data <- mt_time_normalize(mt_data)
```

```{r mt measures, echo=FALSE}

# Calculate distance traveled, velocity, and acceleration for each logged position
normalised_data <- mt_derivatives(normalised_data)

# Calculate minima, maxima, and flips for each dimension, and different measures for curvature (e.g., MAD, AD, and AUC).
normalised_data <- mt_measures(normalised_data)
```

```{r reshaping data, echo=FALSE}

# Reshape data so that the mousetrap object represents the confidence ratitings
reshaped_data <- normalised_data %>% mt_reshape(
  use = "measures",
  use2 = "data",
  use2_variables = c("confidence_rating", "Condition", "subject_nr", "Exemplar"),
  aggregate = FALSE)

#print(reshaped_data)
```

# Analysis

## Visual Inspection of aggregate time-normalised trajectories
```{r aggregate plot, echo = FALSE}

agg_plot <- mt_plot_aggregate(
  normalised_data, 
  use = "tn_trajectories", 
  # points = TRUE,
  x = "xpos", 
  y = "ypos", 
  color = "Condition", 
  #subject_id = "subject_nr"
) + scale_color_manual(values=c("darkorange","steelblue")) + labs(
  title = "Aggregated normalised trajectories per Condition"
  )# +
  #theme(legend.position = c(.2,.2))

print(agg_plot)
```

## Checking sampling rate
```{r sampling rate, echo = FALSE}

sampling_rate <- mt_check_resolution(normalised_data, use = "trajectories",
timestamps = "timestamps", desired = NULL)


print(sampling_rate)
```

## Calculating aggregate measures per Condition
```{r aggregate conditions, echo=FALSE}


agg_conditions <- reshaped_data %>%
  group_by(Condition) %>%
  select(RT, vel_max_time, AUC, confidence_rating) %>%
  summarise(
    rt_mean = mean(RT), rt_sd = sd(RT),
    vmt_mean = mean(vel_max_time), vmt_sd = sd(vel_max_time),
    auc_mean = mean(abs(AUC)), auc_sd = sd(abs(AUC)),
    conf_mean = mean(confidence_rating), conf_sd = sd(confidence_rating)
  ) %>% full_join(correctness_conditions)

print(agg_conditions)

#write.table(agg_conditions, "Aggregated_Measures_Conditions", sep = ",")

```


## Calculating aggregate measures per Exemplar
```{r aggregate exemplars, echo=FALSE}

agg_exemplars <- reshaped_data %>%
  group_by(Exemplar, Condition) %>%
  select(RT, vel_max_time, AUC, confidence_rating) %>%
  summarise(
    rt_mean = mean(RT), rt_sd = sd(RT),
    vmt_mean = mean(vel_max_time), vmt_sd = sd(vel_max_time),
    auc_mean = mean(abs(AUC)), auc_sd = sd(abs(AUC)),
    conf_mean = mean(confidence_rating), conf_sd = sd(confidence_rating)
  ) %>% full_join(correctness_exemplars) %>% ungroup()

print(agg_exemplars)

write.table(agg_exemplars, "Aggregated_Measures_Exemplars", sep = ",")
```

## Checking for Covariance / Correlation
### Covariance Matrix, Aggregated per Condition
```{r cov matrix conds, echo=FALSE}

cov_conditions <- agg_conditions %>%
  select(correct_mean, rt_mean, vmt_mean, auc_mean, conf_mean) %>%
  cov()

print(cov_conditions)

write.table(cov_conditions, "Covariance_conditions", sep = ",")
```

### Covariance Matrix, Aggregated per Exemplar
#### Atypical
```{r cov matrix atypical, echo=FALSE}

cov_atyp <- agg_exemplars %>% filter(Condition == "Atypical") %>%
  select(correct_mean, rt_mean, vmt_mean, auc_mean, conf_mean) %>% 
  cov()

print(cov_atyp)
write.table(cov_atyp, "Covariance_atypical", sep = ",")

```

#### Typical
```{r cov matrix typical, echo = FALSE}

cov_typ <- agg_exemplars %>% filter(Condition == "Typical") %>%
  select(correct_mean, rt_mean, vmt_mean, auc_mean, conf_mean) %>% 
  cov()

print(cov_typ)
write.table(cov_typ, "Covariance_typical", sep = ",")

```

#### Weighted average
```{r cov matrix exemplars, echo = FALSE}
cov_exemplars <- agg_exemplars %>%
  select(correct_mean, rt_mean, vmt_mean, auc_mean, conf_mean) %>%
  cov()

print(cov_exemplars)
write.table(cov_exemplars, "Covariance_exemplars", sep = ",")
```

### Correlation Matrix, Aggregated per Condition
```{r cor matrix conditions, echo = FALSE}

cor_conditions <- agg_conditions %>%
  select(correct_mean, rt_mean, vmt_mean, auc_mean, conf_mean) %>%
  cor()

print(cor_conditions)
write.table(cor_conditions, "Correlation_conditions", sep = ",")

```

### Correlation Matrix, Aggregated per Exemplar
#### Atypical
```{r cor matrix atypical, echo=FALSE}

cor_atyp <- agg_exemplars %>% 
  filter(Condition == "Atypical") %>% 
  select(correct_mean, rt_mean, vmt_mean, auc_mean, conf_mean) %>% 
  cor()

print(cor_atyp)
write.table(cor_atyp, "Correlation_atypical", sep = ",")
```

#### Typical
```{r cor matrix typical, echo = FALSE}

cor_typ <- agg_exemplars %>% 
  filter(Condition == "Typical") %>% 
  select(correct_mean, rt_mean, vmt_mean, auc_mean, conf_mean) %>% 
  cor()

print(cor_typ)
write.table(cor_typ, "Correlation_typical", sep = ",")

```

#### Weighted average
```{r cor matrix exemplars, echo= FALSE}

cor_exemplars <- agg_exemplars %>% 
  select(correct_mean, rt_mean, vmt_mean, auc_mean, conf_mean) %>% 
  cor()

print(cor_exemplars)
write.table(cor_exemplars, "Correlation_exemplars", sep = ",")

```

# Selected Plots
## Hypothesis 1: Mean Confidence is higher for Typical Exemplars

### Per Condition
```{r jitter confidence, echo=FALSE}

jitter_confidence <- reshaped_data %>%
  ggplot(
    aes(
      x = Condition,
      y = confidence_rating,
      color = Condition
    )
  ) + geom_jitter(
    shape = 20,
    size = 5,
    alpha = 0.2,
    width = 0.1
  ) + scale_color_manual(values = c("darkorange", "steelblue")) + labs(
    x = "Conditions",
    y = "Confidence",
    title = "Confidence of Participants per Condition"
  )

print(jitter_confidence)
```

```{r barplot confidence conditions, echo=FALSE}

bar_conf <- agg_conditions %>%
  ggplot(
    aes(
      x = Condition,
      y = conf_mean,
      fill = Condition
    )
  ) + geom_col(color = "black", width = 0.5) + 
  scale_fill_manual(values=c("darkorange","steelblue")) + 
  geom_errorbar(
    aes(
      x = Condition,
      ymin = conf_mean - conf_sd,
      ymax = conf_mean + conf_sd,
      width = 0.4
    )
  ) + labs(
    x = "Condition",
    y = "Confidence",
    title = "Mean Confidence per Condition"
  ) + theme(legend.position = "none")

print(bar_conf)
```

### Per Exemplar

```{r mean conf per exemplar, echo=FALSE}

conf_exemplars <- agg_exemplars %>% 
  ggplot(
    aes(
      x = Exemplar,
      y = conf_mean,
      fill = Condition
    )
  ) + geom_col(
    color = "black",
    width = 0.7
  ) + scale_fill_manual(
    values=c("darkorange","steelblue")
  ) + geom_errorbar(
    aes(
      x = Exemplar,
      ymin = conf_mean - conf_sd,
      ymax = conf_mean + conf_sd,
      width = 0.4
    )
  ) + scale_x_discrete(labels = 1:19) + labs(
    x = "Exemplars",
    y = "Confidence",
    title = "Mean Confidence per Exemplar"
  ) 

print(conf_exemplars)

```

## Hypothesis 2: Higher correctness ratio for Typical Exemplars

### Per Condition
```{r barplot correctness, echo = FALSE}

bar_correct <- agg_conditions %>%
  ggplot(
    aes(
      x = Condition,
      y = correct_mean,
      fill = Condition
    )
  ) + geom_col(color = "black", width = 0.5) + scale_fill_manual(values=c("darkorange","steelblue")) + geom_errorbar(
    aes(
      x = Condition,
      ymin = correct_mean - correct_sd,
      ymax = correct_mean + correct_sd,
      width = 0.4
    )
  ) + labs(
    x = "Condition",
    y = "Ratio of correct answers",
    title = "Correctness Ratio per Condition"
  ) + theme(legend.position = "none")

print(bar_correct)

```

### Per Exemplar

```{r correctness ratio exemplar, echo=FALSE}

correct_ratio_exemplars <- agg_exemplars %>% 
  ggplot(
    aes(
      x = Exemplar,
      y = correct_mean,
      fill = Condition
    )
  ) + geom_col(
    color = "black",
    width = 0.7
  ) + scale_fill_manual(
    values=c("darkorange","steelblue")
  ) + geom_errorbar(
    aes(
      x = Exemplar,
      ymin = correct_mean - correct_sd,
      ymax = correct_mean + correct_sd,
      width = 0.4
    )
  ) + scale_x_discrete(labels = 1:19) + labs(
    x = "Exemplars",
    y = "Ratio of correct answers",
    title = "Correctness Ratio per Exemplar"
  ) 

print(correct_ratio_exemplars)

```

## Hypothesis 3: Mean RT is lower for Typical Exemplars

### Per Condition
```{r jitter RT, echo=FALSE}

jitter_RT <- reshaped_data %>% 
  ggplot(
    aes(
      x = Condition,
      y = RT,
      color = Condition
    )
  ) + geom_jitter(
    shape = 20,
    size = 5,
    alpha = 0.2,
    width = 0.1
  ) + scale_color_manual(values = c("darkorange", "steelblue")) + labs(
    x = "Conditions",
    y = "Time in ms",
    title = "Response Times per Condition"
  )

print(jitter_RT)

```

```{r barplot rt conditions, echo=FALSE}

bar_RT <- agg_conditions %>%
  ggplot(
    aes(
      x = Condition,
      y = rt_mean,
      fill = Condition
    )
  ) + geom_col(
    color = "black",
    width = 0.5
  ) + scale_fill_manual(values=c("darkorange","steelblue")) + geom_errorbar(
    aes(
      x = Condition,
      ymin = rt_mean - rt_sd,
      ymax = rt_mean + rt_sd,
      width = 0.4
    )
  ) + labs(
    x = "Condition",
    y = "Time in ms",
    title = "Mean Response Times per Condition"
  ) + theme(legend.position = "none")

print(bar_RT)

```


### Per Exemplar

```{r mean RT per exemplar, echo = FALSE}

rt_exemplar <- agg_exemplars %>%
  ggplot(
    aes(
      x = Exemplar,
      y = rt_mean,
      fill = Condition
    )
  ) + geom_col(
    color = "black",
    width = 0.7
  ) + scale_fill_manual(
    values=c("darkorange","steelblue")
  ) + geom_errorbar(
    aes(
      x = Exemplar,
      ymin = rt_mean - rt_sd,
      ymax = rt_mean + rt_sd,
      width = 0.4
    )
  ) + scale_x_discrete(labels = 1:19) + labs(
    x = "Exemplar",
    y = "Time in ms",
    title = "Mean RTs per Exemplar"
  )

print(rt_exemplar)

```

## Hypothesis 4: Mean vel_max_time is lower for Typical Exemplars

### Per Condition
```{r jitter vmt, echo=FALSE}

jitter_vmt <- reshaped_data %>%
  ggplot(
    aes(
      x = Condition,
      y = vel_max_time,
      color = Condition
    )
  ) + geom_jitter(
    shape = 20,
    size = 5,
    alpha = 0.2,
    width = 0.1
  ) + scale_color_manual(values = c("darkorange", "steelblue")) + labs(
    x = "Conditions",
    y = "Time in ms",
    title = "vel_max_time per Condition"
  )

print(jitter_vmt)
```

```{r barplot vmt conditions, echo=FALSE}

bar_vmt <- agg_conditions %>%
  ggplot(
    aes(
      x = Condition,
      y = vmt_mean,
      fill = Condition
    )
  ) + geom_col(
    color = "black", 
    width = 0.5
  ) + scale_fill_manual(values=c("darkorange","steelblue")) + geom_errorbar(
    aes(
      x = Condition,
      ymin = vmt_mean - vmt_sd,
      ymax = vmt_mean + vmt_sd,
      width = 0.4
    )
  ) + labs(
    x = "Condition",
    y = "Time in ms",
    title = "Mean vel_max_time per Condition"
  ) + theme(legend.position = "none")

print(bar_vmt)

```

### Per Exemplar

```{r mean vmt per exemplar, echo = FALSE}

vmt_exemplar <- agg_exemplars %>%
  ggplot(
    aes(
      x = Exemplar,
      y = vmt_mean,
      fill = Condition
    )
  ) + geom_col(
    color = "black",
    width = 0.7
  ) + scale_fill_manual(
    values=c("darkorange","steelblue")
  ) + geom_errorbar(
    aes(
      x = Exemplar,
      ymin = vmt_mean - vmt_sd,
      ymax = vmt_mean + vmt_sd,
      width = 0.4
    )
  ) + scale_x_discrete(labels = 1:19) + labs(
    x = "Exemplar",
    y = "Time in ms",
    title = "Mean vel_max_time per Exemplar"
  ) 

print(vmt_exemplar)

```

## Hypothesis 5: Mean AUC is lower for Typical Exemplars

### Per Condition
```{r jitter auc, echo=FALSE}

jitter_auc <- reshaped_data %>%
  ggplot(
    aes(
      x = Condition,
      y = abs(AUC),
      color = Condition
    )
  ) + geom_jitter(
    shape = 20,
    size = 5,
    alpha = 0.2,
    width = 0.1
  ) + scale_color_manual(values = c("darkorange", "steelblue")) + labs(
    x = "Conditions",
    y = "AUC",
    title = "AUC per Condition"
  )

print(jitter_auc)
```

```{r barplot auc conditions, echo=FALSE}

bar_auc <- agg_conditions %>%
  ggplot(
    aes(
      x = Condition,
      y = auc_mean,
      fill = Condition
    )
  ) + geom_col(
    color = "black", 
    width = 0.5
  ) + scale_fill_manual(values=c("darkorange","steelblue")) + geom_errorbar(
    aes(
      x = Condition,
      ymin = auc_mean - auc_sd,
      ymax = auc_mean + auc_sd,
      width = 0.4
    )
  ) + labs(
    x = "Condition",
    y = "Mean AUC",
    title = "Mean AUC per Condition"
  ) + theme(legend.position = "none")

print(bar_auc)
```

### Per Exemplar

```{r mean auc per exemplar, echo = FALSE}

auc_exemplar <- agg_exemplars %>%
  ggplot(
    aes(
      x = Exemplar,
      y = abs(auc_mean),
      fill = Condition
    )
  ) + geom_col(
    color = "black",
    width = 0.7
  ) + scale_fill_manual(
    values=c("darkorange","steelblue")
  ) + geom_errorbar(
    aes(
      x = Exemplar,
      ymin = abs(auc_mean) - abs(auc_sd),
      ymax = abs(auc_mean) + abs(auc_sd),
      width = 0.4
    )
  ) + scale_x_discrete(labels = 1:19) + labs(
    x = "Exemplar",
    y = "Mean AUC",
    title = "Mean AUC per Exemplar"
  ) 

print(auc_exemplar)

```

## Correlation Plots

### Confidence / RT

```{r jitter RT/confidence, echo=FALSE}

reshaped_data %>% 
  ggplot(
    aes(
      x = RT,
      y = confidence_rating,
      color = Condition
    )
  ) + geom_jitter(
    shape = 20,
    size = 7,
    alpha = 0.2,
    width = 0.1
  ) + scale_color_manual(
    values = c("darkorange", "steelblue")
  )  + geom_smooth(
    method = lm,
    se = F,
    color = "black"
  ) + labs(
    x = "Response Time in ms",
    y = "Confidence",
    title = "Correlation of Confidence Ratings and Response Times"
  )

```


### Confidence / vel_max_time

```{r jitter vmt/confidence, echo=FALSE}

reshaped_data %>% 
  ggplot(
    aes(
      x = vel_max_time,
      y = confidence_rating,
      color = Condition
    )
  ) + geom_jitter(
    shape = 20,
    size = 7,
    alpha = 0.2,
    width = 0.1
  ) + scale_color_manual(
    values = c("darkorange", "steelblue")
  ) + geom_smooth(
    method = lm,
    se = F,
    color = "black"
  ) + labs(
    x = "vel_max_time in ms",
    y = "Confidence",
    title = "Correlation of Confidence Ratings and vel_max_time"
  )

```


### Confidence / AUC

```{r jitter auc/confidence, echo=FALSE}

reshaped_data %>% 
  ggplot(
    aes(
      x = abs(AUC),
      y = confidence_rating,
      color = Condition
    )
  ) + geom_jitter(
    shape = 20,
    size = 7,
    alpha = 0.2,
    width = 0.1
  ) + scale_color_manual(
    values = c("darkorange", "steelblue")
  ) + geom_smooth(
    method = lm,
    se = F,
    color = "black"
  ) + labs(
    x = "AUC",
    y = "Confidence",
    title = "Correlation of Confidence Ratings and AUC"
  ) 

```


## Generating Heatmaps

### Plotting Individual Trajectories
```{r all trajectories, echo=FALSE}

mt_heatmap(
  normalised_data,
  xres = 1000,
  colors = c("white", "black")
) 

```

### Generating smoothed Heatmap
```{r smooth heatmap, echo=FALSE}

mt_heatmap(
  normalised_data,
  xres = 1000,
  colors = c("white", "black"),
  smooth_radius = 20,
  n_shades = 10,
  mean_image = 0.2
)

```

### Generating Difference Heatmap
```{r diffmap, echo=FALSE}

mt_diffmap(
  normalised_data,
  xres = 1000,
  condition = "Condition",
  colors = c("darkorange", "white", "steelblue"), #1st = atyp, 2nd = bg, 3rd = typ
  smooth_radius = 20,
  n_shades = 10
)

```
# Supplementary Plots

## Data Distribution Plots

### Response Times

```{r jitter RT, echo=FALSE}

reshaped_data %>% 
  ggplot(
    aes(
      x = Condition,
      y = RT,
      color = Condition
    )
  ) + geom_jitter(
    shape = 20,
    size = 5,
    alpha = 0.2,
    width = 0.1
  ) + scale_color_manual(values = c("darkorange", "steelblue")) + labs(
    x = "Conditions",
    y = "RT in ms",
    title = "Response Times per Condition"
  ) + theme(legend.position = "none")
```

```{r violin RT, echo = FALSE}

reshaped_data %>%
  ggplot(
    aes(
      x = Condition,
      y = RT,
      fill = Condition
    )
  ) + geom_violin() + scale_fill_manual(values=c("darkorange","steelblue")) + labs(
    x = "Condition",
    y = "RTs in ms",
    title = "Response Times per Condition"
  ) + theme(legend.position = "none")

```

```{r scatter RT exemplars, echo = FALSE}

exemplars_full %>% 
  ggplot(
    aes(
      x = Exemplar,
      y = RT,
      color = Condition
    )
  ) + geom_point(
    shape = 20,
    size = 5,
    alpha = 0.2,
    width = 0.1
  ) + scale_color_manual(
    values = c("darkorange", "steelblue")
  ) + scale_x_discrete(labels = 1:19) + labs(
    x = "Exemplars",
    y = "Response Time in ms",
    title = "Response Times per Exemplar"
  ) + theme(
    axis.title = element_text(size=9),
    plot.title = element_text(size=11)
  )

```

### vel_max_time

```{r jitter vmt, echo=FALSE}
reshaped_data %>%
  ggplot(
    aes(
      x = Condition,
      y = vel_max_time,
      color = Condition
    )
  ) + geom_jitter(
    shape = 20,
    size = 5,
    alpha = 0.2,
    width = 0.1
  ) + scale_color_manual(values = c("darkorange", "steelblue")) + labs(
    x = "Conditions",
    y = "vel_max_time in ms",
    title = "vel_max_time per Condition"
  ) + theme(legend.position = "none")
```

```{r violin vmt, echo = FALSE}

reshaped_data %>%
  ggplot(
    aes(
      x = Condition,
      y = vel_max_time,
      fill = Condition
    )
  ) + geom_violin() + scale_fill_manual(values=c("darkorange","steelblue")) + labs(
    x = "Condition",
    y = "vel_max_time in ms",
    title = "vel_max_time per Condition"
  ) + theme(legend.position = "none")

```

```{r scatter vmt exemplars, echo=FALSE}

exemplars_full %>% 
  ggplot(
    aes(
      x = Exemplar,
      y = vel_max_time,
      color = Condition
    )
  ) + geom_point(
    shape = 20,
    size = 5,
    alpha = 0.2,
    width = 0.1
  ) + scale_color_manual(
    values = c("darkorange", "steelblue")
  ) + scale_x_discrete(labels = 1:19) + labs(
    x = "Exemplars",
    y = "vel_max_time in ms",
    title = "vel_max_time per Exemplar"
  ) + theme(
    axis.title = element_text(size=9),
    plot.title = element_text(size=11)
  )

```

### AUC

```{r jitter auc, echo=FALSE}
reshaped_data %>%
  ggplot(
    aes(
      x = Condition,
      y = abs(AUC),
      color = Condition
    )
  ) + geom_jitter(
    shape = 20,
    size = 5,
    alpha = 0.2,
    width = 0.1
  ) + scale_color_manual(values = c("darkorange", "steelblue")) + labs(
    x = "Conditions",
    y = "AUC",
    title = "AUC per Condition"
  ) + theme(legend.position = "none")
```

```{r violin AUC, echo = FALSE}

reshaped_data %>%
  ggplot(
    aes(
      x = Condition,
      y = abs(AUC),
      fill = Condition
    )
  ) + geom_violin() + scale_fill_manual(values=c("darkorange","steelblue")) + labs(
    x = "Condition",
    y = "AUC",
    title = "AUC per Condition"
  ) + theme(legend.position = "none")

```

```{r scatter auc exemplars, echo=FALSE}

exemplars_full %>% 
  ggplot(
    aes(
      x = Exemplar,
      y = abs(AUC),
      color = Condition
    )
  ) + geom_point(
    shape = 20,
    size = 5,
    alpha = 0.2,
    width = 0.1
  ) + scale_color_manual(
    values = c("darkorange", "steelblue")
  ) + scale_x_discrete(labels = 1:19) + labs(
    x = "Exemplars",
    y = "AUC",
    title = "AUC per Exemplar"
  ) + theme(
    axis.title = element_text(size=9),
    plot.title = element_text(size=11)
  )

```

### Confidence

```{r jitter confidence, echo=FALSE}
additional_measures %>%
  ggplot(
    aes(
      x = Condition,
      y = confidence_rating,
      color = Condition
    )
  ) + geom_jitter(
    shape = 20,
    size = 5,
    alpha = 0.2,
    width = 0.1
  ) + scale_color_manual(values = c("darkorange", "steelblue")) + labs(
    x = "Conditions",
    y = "Confidence",
    title = "Confidence per Condition"
  ) + theme(legend.position = "none")
```

```{r violin confidence, echo = FALSE}

reshaped_data %>%
  ggplot(
    aes(
      x = Condition,
      y = confidence_rating,
      fill = Condition
    )
  ) + geom_violin() + scale_fill_manual(values=c("darkorange","steelblue")) + labs(
    x = "Condition",
    y = "Confidence Rating",
    title = "Confidence per Condition"
  ) + theme(legend.position = "none")

```

```{r jitter conf exemplars, echo = FALSE}

exemplars_full %>% 
  ggplot(
    aes(
      x = Exemplar,
      y = confidence_rating,
      color = Condition
    )
  ) + geom_jitter(
    shape = 20,
    size = 5,
    alpha = 0.2,
    width = 0.1
  ) + scale_color_manual(
    values = c("darkorange", "steelblue")
  ) + scale_x_discrete(labels = 1:19) + labs(
    x = "Exemplars",
    y = "Confidence",
    title = "Confidence per Exemplar"
  ) + theme(
    axis.title = element_text(size=9),
    plot.title = element_text(size=11)
  )

```

## Correlation Plots

```{r jitter RT/confidence atypical, echo = FALSE}
reshaped_data %>% filter(Condition == "Atypical") %>%
  ggplot(
    aes(
      x = RT,
      y = confidence_rating
    )
  ) + geom_jitter(
    shape = 20,
    size = 7,
    alpha = 0.2,
    width = 0.1,
    colour = "darkorange"
  ) + geom_smooth(
    method = lm,
    se = F,
    color = "black"
  ) + labs(
    x = "Response Time in ms",
    y = "Confidence",
    title = "Correlation of Confidence Ratings and Response Times",
    subtitle = "Atypical Condition"
  ) 

```

```{r jitter RT/confidence typical}

reshaped_data %>% filter(Condition == "Typical") %>%
  ggplot(
    aes(
      x = RT,
      y = confidence_rating
    )
  ) + geom_jitter(
    shape = 20,
    size = 7,
    alpha = 0.2,
    width = 0.1,
    colour = "steelblue"
  ) + geom_smooth(
    method = lm,
    se = F,
    color = "black"
  ) + labs(
    x = "Response Time in ms",
    y = "Confidence",
    title = "Correlation of Confidence Ratings and Response Times",
    subtitle = "Typical Condition"
  )
```

```{r jitter vmt/confidence atypical, echo=FALSE}

reshaped_data %>% filter(Condition == "Atypical") %>%
  ggplot(
    aes(
      x = vel_max_time,
      y = confidence_rating
    )
  ) + geom_jitter(
    shape = 20,
    size = 7,
    alpha = 0.2,
    width = 0.1,
    colour = "darkorange"
  ) + geom_smooth(
    method = lm,
    se = F,
    color = "black"
  ) + labs(
    x = "vel_max_time in ms",
    y = "Confidence",
    title = "Correlation of Confidence Ratings and vel_max_time",
    subtitle = "Atypical Condition"
  )

```

```{r jitter vmt/confidence typical, echo = FALSE}  
reshaped_data %>% filter(Condition == "Typical") %>%
  ggplot(
    aes(
      x = vel_max_time,
      y = confidence_rating
    )
  ) + geom_jitter(
    shape = 20,
    size = 7,
    alpha = 0.2,
    width = 0.1,
    colour = "steelblue"
  ) + geom_smooth(
    method = lm,
    se = F,
    color = "black"
  ) + labs(
    x = "vel_max_time in ms",
    y = "Confidence",
    title = "Correlation of Confidence Ratings and vel_max_time",
    subtitle = "Typical Condition"
  )
```

```{r jitter auc/confidence atypical, echo = FALSE}
reshaped_data %>% filter(Condition == "Atypical") %>%
  ggplot(
    aes(
      x = abs(AUC),
      y = confidence_rating
    )
  ) + geom_jitter(
    shape = 20,
    size = 7,
    alpha = 0.2,
    width = 0.1, 
    colour = "darkorange"
  ) + geom_smooth(
    method = lm,
    se = F,
    color = "black"
  ) + labs(
    x = "AUC",
    y = "Confidence",
    title = "Correlation of Confidence Ratings and AUC",
    subtitle = "Atypical Condition"
  )

```

```{r jitter auc/confidence typical, echo = FALSE}

reshaped_data %>% filter(Condition == "Typical") %>%
  ggplot(
    aes(
      x = abs(AUC),
      y = confidence_rating
    )
  ) + geom_jitter(
    shape = 20,
    size = 7,
    alpha = 0.2,
    width = 0.1, 
    colour = "steelblue"
  ) + geom_smooth(
    method = lm,
    se = F,
    color = "black"
  ) + labs(
    x = "AUC",
    y = "Confidence",
    title = "Correlation of Confidence Ratings and AUC",
    subtitle = "Typical Condition"
  )

```